\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvtheme[blue]{casual}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.88]{geometry}


%change shading of name to make firstname darker
\usepackage{etoolbox}
\patchcmd{\makecvtitle}{\color{color2!50}\@firstname}{\color{color2}\@firstname}{}{}
\patchcmd{\makecvtitle}{\color{color2}\@lastname}{\color{color2!50}\@lastname}{}{}

%Personal Data
\firstname{Eric}
\lastname{Lin}
%\title{Curriculum Vitae}                           % optional, remove / comment the line if not wanted
\address{318 Elmwood Ave Unit 2}{Ithaca, NY 14853}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\mobile{571-594-6663}                          % optional
\email{esl89@cornell.edu}                               % optional
%\homepage{www.johndoe.com}                         % optional
%\extrainfo{}             % optional
%\photo[64pt][0.4pt]{example-image-a}              % optional


\begin{document}
\makecvtitle
\vspace*{-15mm}  %control space under the cvtitle

\section{Education}
\cventry{2013--2017}{BS in Computer Science}{Cornell University}{Ithaca, NY}{\textit{GPA: 3.82/4.0}}{Minor in Business}  % arguments 3 to 6 can be left empty
\cventry{2013}{High School Diploma}{Thomas Jefferson High School for Science and Tech}{Alexandria, VA}{}{}{}{}



\section{Leadership Experience}

\cventry{Fall 2015}{Vice President}{Association of Computer Science Undergraduates}{}{}{
- Scheduled and coordinated information sessions for over 20 tech companies hosted on campus. \newline{}
- Managed regular club activities such as social events, resume book, and executive board meetings. \newline{}
- Launched club initiatives such as Mentorship.}

\cventry{Fall 2015}{CS3110 Functional Programming Teaching Assistant}{Cornell University}{Ithaca, NY}{}{
- Led recitations  on course material, held office hours, and graded programming assignments and exams.}


\section{Work Experience}

\cventry{Summer 2015}{Software Development Intern}{Epic}{Madison, WI}{}{
- Designed and implemented an algorithm and accompanying interface for assigning nurses to inpatients to maximize nurse satisfaction and quality of patient care. \newline{}
- Applied our model to work with any hospital system and integrated it into Epic's framework. \newline{}
- Developed primarily in C\# and Javascript, created design documentation and UI mockups. }

\cventry{Summer 2014}{Quality Assurance Intern}{B-Line Medical, L.L.C.}{Washington, D.C}{}{
- Built an accounting database application using Node.JS, HTML, Javascript, and SQLite. \newline{}
- Created automated tests for basic CRUD operations using Selenium web driver and Jasmine. \newline{} 
- Learned general software design principles like version control via Git and code documentation. }

\cventry{Summer 2012}{Web Development Intern}{International Fund for China's Environment}{Washington, D.C}{}{
- Collaborated with a design student to create a website using HTML, CSS, Javascript, and PHP. \newline{}
- Built in a contact page with email capabilities, and a registration form for an upcoming event. \newline{} 
- Communicated with the organization regularly to determine preferred features of the site at each deadline.
}

\section{Extracurriculars}

\cventry{Spring 2015}{Academic Excellence Workshop Facilitator}{Object-Oriented Programming \& Data Structures}{}{}{
- Prepared and presented weekly lectures and problem sets based on and supplementing course material.}

\cventry{2013-2015}{Business Analyst}{Cornell Strategic Consulting}{}{}{
- Worked with local startups and small businesses to provide services such as market research, competitor analysis, financial planning, pricing models, and strategic recommendations.}



\section{Projects}

\cvline{Tag!}{First person Virtual Reality Horror-Shooter game. Oculus Rift, Leap Motion, and Unity Game Engine (C\#, Javascript), created at BrickHack. }

\cvline{PokeMatch} {iOS tile matching game. Player can clear two matching tiles if there exists a path with less than 3 turns between them, implemented with heuristic BFS algorithm. Swift.}

\cvline{Cornell Strategic Consulting}{Designed and developed a website for the club to increase online presence. Created an application page that increased new member applications over 30\% in its first week. HTML, Javascript, PHP.}

\section{Programming Skills}
\cvline{Languages}{Java, Javascript, OCaml, C\#, Python, HTML/CSS}
\cvline{Databases}{SQLite}
\cvline{Tools}{Node.JS, Git, iOS}


\end{document}